Cover Letter: Cudele (Paper 306)

### 2018-02-28 paper/sections/2_related_work.tex
paper: typos and acknowledgements
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% Non POSIX IO
High performance computing has unique requirements for file systems ({\it
e.g.}, fast creates) and well-defined workloads ({\it e.g.}, workflows) that
make relaxing POSIX IO sensible.  BatchFS assumes the application coordinates
accesses to the namespace, so the clients can batch local operations and merge
with a global namespace image lazily. Similarly, DeltaFS eliminates RPC
traffic using subtree snapshots for non-conflicting workloads and middleware
for conflicting workloads. MarFS gives users the ability to lock
``project directories" and allocate GPFS clusters for demanding metadata
workloads. TwoTiers eliminates high-latencies by storing metadata in a flash
tier; applications lock the namespace so that metadata can be accessed more quickly.
Unfortunately, decoupling the namespace has costs: (1) merging metadata state
back into the global namespace is slow; (2) failures are local to the failing
node; and (3) the systems are not backwards compatible.

>>>>

% Non POSIX IO
High performance computing has unique requirements for file systems and
well-defined workloads that make relaxing POSIX IO sensible.  BatchFS assumes
the application coordinates accesses to the namespace, so the clients can batch
local operations and merge with a global namespace image lazily. Similarly,
DeltaFS eliminates RPC traffic using subtree snapshots for non-conflicting
workloads and middleware for conflicting workloads.
MarFS~\cite{grider:pdsw2015-marfs} gives users the ability to lock ``project
directories" and allocate clusters for demanding metadata workloads.
TwoTiers~\cite{bent:slides-twotiers} eliminates high-latencies by storing
metadata in a flash tier; applications lock the namespace so that metadata can
be accessed more quickly.  Unfortunately, decoupling the namespace has costs:
(1) merging metadata state back into the global namespace is slow; (2) failures
are local to the failing node; and (3) the systems are not backwards
compatible.

### 2018-02-28 paper/sections/6_results.tex
paper: typos and acknowledgements
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark, shvachko:login2012-hdfs-scalability}; Big Data Benchmark jobs
examined in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens
or creates just to start a single Spark query and the Lustre system they tested
on did not handle creates well, showing up to a \(24\times\) slowdown compared
to other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system, like BatchFS or DeltaFS, that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}

>>>>

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark}; Big Data Benchmark jobs examined
in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens or
creates just to start a single Spark query and the Lustre system they tested on
did not handle creates well, showing up to a \(24\times\) slowdown compared to
other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system, like BatchFS or DeltaFS, that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}
